COG-ED Manuscript

### 2022-01-14 06_Paper/COG-ED/Manuscript.Rmd
nicely panelled sca plot

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
    geom_line(aes(group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign)) +
    geom_text(x = 3, y = -0.01, label = "NFC") +
    geom_text(x = 3, y = -0.12, label = "Level") +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(lim = c(NA,0.01), breaks = c(-0.10,-0.05,0), labels = c("-0.10", "-0.05", "Fixed effects \u03b2  0.00")) +
    theme(axis.text.x = element_blank(), legend.position = "none")

@@

@@

  sca_lowerplot <- ggplot(data = sca_results) +
    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
    geom_point(aes(x = num, y = Dim)) +
    geom_point(aes(x = num, y = Trans)) +
    geom_point(aes(x = num, y = Excl)) +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_reverse(breaks = c(1:17), lim = c(17,0), labels = c(expression(bold("Dimension")),
                                                                "Across S, across C", "Across S, within C",
                                                                "Within S, within C", "Within S, across C",
                                                                expression(bold("Transformation")),
                                                                "Raw/None", "Log", "Inverse", "Square-root",
                                                                expression(bold("Exclusion")),
                                                                "None", "2 MAD from median", "2.5 MAD from median",
                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
    theme(axis.text.x = element_blank(), legend.position = "none")

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # for great tables in R Markdown
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable
# library(glmmTMB)      # from the glmmTMB package for multi level models
  library(BayesFactor)  # computing Bayes factors, "BayesFactor" package
  library(ggplot2)      # for plotting, "ggplot2" package
  library(egg)          # for paneling plots, "egg" package

@@

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta)) +
    geom_line(aes(group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign)) +
    geom_text(x = 3, y = -0.01, label = "NFC") +
    geom_text(x = 3, y = -0.12, label = "Level") +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate \u03b2") +
    scale_y_continuous(lim = c(NA,0.01)) +
    theme(axis.text.x = element_blank(),
          axis.line.y = element_line(size = 1, color = "black"), axis.title.y = element_text(margin = margin(r = 10)),
          legend.position = "none")

@@

  sca_lowerplot <- ggplot(data = sca_results) +
    geom_hline(yintercept = c(1,6,11), color = "grey", size = 0.5) +
    geom_hline(yintercept = c(2:5,7:10,12:17), color = "grey", linetype = "dashed", size = 0.2) +
    geom_point(aes(x = num, y = Dim)) +
    geom_point(aes(x = num, y = Trans)) +
    geom_point(aes(x = num, y = Excl)) +
    theme_classic() +
    labs(x = "Analysis pipeline", y = NULL) +
    scale_y_reverse(breaks = c(1:17), lim = c(17,0.5), labels = c(expression(bold("Dimension")),
                                                                "Across S, across C", "Across S, within C",
                                                                "Within S, within C", "Within S, across C",
                                                                expression(bold("Transformation")),
                                                                "Raw/None", "Log", "Inverse", "Square-root",
                                                                expression(bold("Exclusion")),
                                                                "None", "2 MAD from median", " 2.5 MAD from median",
                                                                "3 MAD from median", "100ms after onset", "200ms after onset")) +
    theme(axis.text.x = element_blank(), axis.title.x = element_text(margin = margin(t = 10)),
          axis.line.y = element_line(size = 1, color = "black"),
          legend.position = "none")

  # put both plots into one

  sca_plot <- ggarrange(sca_upperplot, sca_lowerplot, nrow = 2, heights = c(1,2.5))
